\bf Approximating Likelihood Ratios with Calibrated Discriminative Classifiers

### 2016-02-11 jasa/paper-jasa.tex
Acknowledgments

>>>>

\section*{Acknowledgements} KC would like to thank Daniel Whiteson for
encouragement throughout the project and Alex Ihler for challenging discussions
that  led to a reformulation of the initial idea. KC would also like to thank
Shimon Whiteson, Babak Shahbaba for advice in the presentation, Radford Neal for
discussion of his earlier work, Yann LeCun, Philip Stark, and Pierre Baldi for
their feedback on the project early in its conception, Bal\'azs K\'egl for
feedback to the draft,  and Yuri
Shirman for reassuring cross checks of the Theorem.  KC is supported by the US
National Science Foundation grants PHY-0854724 and PHY-0955626.  KC is grateful
to UC-Irvine for their hospitality while this research was carried out and the
Moore and Sloan foundations for their generous support of the data science
environment at NYU.
\glnote{Update the acknowlegdments? What do we need to mention regarding my financial support?}
